### 2022-01-27 manuscript/manuscript.Rmd
Add new results regarding the regressions comparison

@@

>>>>

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{fig2.png}
		\caption{INSERT CAPTION}
	\end{measuredfigure}
\end{figure}

@@

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{fig3.png}
		\caption{INSERT CAPTION}
	\end{measuredfigure}
\end{figure}

Although the accuracy of our equations showed to be beyond the established 8\% threshold, when applying a model not developed for jumping activies we can se that the accuracy tremendously decreases, reaching values of MAPE around `r floor(mean(as.numeric(substr(tab2_df$MAPE, 1, nchar(tab2_df$MAPE) - 2))[1:4]) / 50) * 50`\% for pGRF prediction and around `r floor(mean(as.numeric(substr(tab2_df$MAPE, 1, nchar(tab2_df$MAPE) - 2))[5:8]) / 10) * 10`\% for pLR prediction as can be observed in Table 2. Furthermore, applying to our accelerometer-recorded jumping data a model that is not specific for this activity yield unresonable results, such as the negative values for pGRF that can be observed in Figure 3, Panel A.
